Cryptographic assurance of secrecy and fairness in voting

### 2012-12-06 paper/paper.tex
Reduce parenthetical statements
Add kremer paper, "observational equivalence" privacy

Delaune \cite{delaune} gives several definitions of ballot secrecy.
In order of increasing strength, they are
\term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.

@@

More formally, we can say that an election system has private ballots
if a reasonably time-bounded attacker, having access to the public information
published by the polling authority ... \todo{}

>>>>

\cite{delaune} enumerates a hierarchy of ballot secrecy definitions.
In order of increasing strength, they are
\term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.

@@

\cite{kremer} gives an \term{observational equivalence} definition of privacy:
An election system is private if an attacker, having access to the public
information published by the polling authority, ``cannot distinguish
the actual situation from one in which two voters have swapped their votes.''

% For all pairs of voters $v_1$, $v_2$ ...
